Fast, Robust Classification with Applications to Periodic Variable Stars

### 2012-05-10 report/ms.tex
converted .png to .pdf
added some results from today. Ranges of C could perhaps be improved.

\subsubsection{Performance}
The performance of the combined SVM model was compared to those of its degenerates by computing expected losses for multiple values of $\lambda$ and $\rho$.  For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint. See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,0.750]$ and $\rho\in\lbrace 0\rbrace\cup [0.090,0.032]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in\lbrace 0\rbrace\cup [0.375,0.750]$. Observe that $(\lambda^*,\rho^*)\neq (0,0)$ for both datasets, which implies that the combined model outperforms both of its degenerates. For the CEP dataset, the optimal $(\lambda^*,\rho^*)=(9,0.320)$ yielded 13.25\% classification error while for the RR dataset, $(\lambda^*,\rho^*)=(284,0.48)$ yielded 21.50\% classification error. THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze_feature.m.

>>>>

\subsubsection{Performance}
The performance of the combined SVM model was compared to those of its degenerates by computing expected losses for multiple values of $\lambda$ and $\rho$.  For a given $(\lambda,\rho)$, the expected loss was computed by performing cross-validation in 90-10 splits so that the union of testing points across splits is the entire dataset and the intersection is disjoint. See surface plots of loss versus $(\lambda,\rho)$: for the CEP dataset, $\lambda\in \lbrace 0\rbrace\cup [0.375,9]$ and $\rho\in\lbrace 0\rbrace\cup [0.90,0.32]$ while for the RR dataset, $\lambda\in\lbrace 0\rbrace\cup [54,284]$ and $\rho\in[0.00,0.48]$. Observe that $(\lambda^*,\rho^*)\neq (0,0)$ for both datasets, which implies that the combined model outperforms both of its degenerates. For the CEP dataset, the optimal $(\lambda^*,\rho^*)=(9,0.320)$ yielded 13.25\% classification error while for the RR dataset, $(\lambda^*,\rho^*)=(284,0.48)$ yielded 21.50\% classification error. THESE NUMBERS DON'T LOOK RIGHT, MUST RERUN analyze_feature.m.
